### 2017-10-10 biosketch/mehedi-nihbiosketch.tex
update biosketch

\begin{statement}
I have the expertise and motivation necessary to successfully carry out the proposed research project.  I have a background in computer science, with specific expertise in health informatics, machine learning, and textual data analytics.  My research includes automatic annotation of clinical text, information extraction from electronic health records for improving the study of cancer risk and outcomes.  As a graduate reserach assistant on several university- and NIH-funded grants, I successfully collaborated with other researchers, and produced the following publications.

@@

Manual encoding has been used to annotate clinical text of motivational interview transcripts for many years, which is time consuming and resource intensive. However, my reserach shown that state-of-the-art machine learning methods can be used as a cheap alternate for the annotation that can facilitate researchers to establish a causal relationship between different communication strategies and desired behavioral outcomes without having to repeatedly wade through pages of interview transcripts.

@@

\grantinfo{NHLBI 1U01HL097889-01}{Naar--King \& Jen (PIs)}{2014-2016}
{Provider Communication Behaviors that Predict Motivation to Change in Black Adolescents with Obesity.}
{The goal of this research was to identify communication behaviors used by weight loss counselors that mostly strongly predicted Black adolescents’ motivational statements.}
{Role: Graduate Research Assistant}

>>>>

\begin{statement}
I have the expertise and motivation necessary to successfully carry out the proposed research project. I have a background in computer science, with specific expertise in health informatics, machine learning, and textual
data analytics. My research includes automatic annotation of clinical text, information extraction from electronic health records for improving the study of cancer risk and outcomes. As a graduate research assistant at several university and NIH-funded grants, I successfully collaborated with other researchers and produced the following publications.

@@

Manual encoding has been used to annotate clinical text of motivational interview transcripts for many years, which is time consuming and resource intensive. However, my research has shown that state-of-the-art machine learning methods can be used as a cheap alternative for the annotation that can facilitate researchers to establish a causal relationship between different communication strategies and desired behavioral outcomes without having to repeatedly wade through pages of interview transcripts.

@@

\grantinfo{NHLBI 1U01HL097889-01}{Naar--King \& Jen (PIs)}{2014-2016}
{Provider Communication Behaviors that Predict Motivation to Change in Black Adolescents with Obesity.}
{The goal of this research was to identify communication behaviors used by weight loss counselors that most strongly predicted Black adolescents’ motivational statements.}
{Role: Graduate Research Assistant}
